---
title: "Quick Start"
author: "Ben Best"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = TRUE, message=F, warning=F)
```

## Install `npstools` & Configure Path to Tables

You only need to run this once, or again to update package.

```{r, eval=F}
library(devtools) # install.packages("devtools")

devtools::install_github("ecoquants/npstools")
```

You'll need access to the databaes tables in comma-seperated value (CSV) format. If you don't have access to the shared drive where they're stored internally, you can use this copy:

- [R_tables_csv.zip](https://drive.google.com/open?id=1NmJjejHnrhvCT-qmnoR-3XHkUTPs7x09)

You'll then need to unzip the contents and create your own configuration file with this path, similar to:

- [nps_config.yaml](https://github.com/ecoquants/npstools/blob/master/inst/nps_config.yaml)

It is recommended that you setup this file in your home directory `"~/nps_config.yaml"` or an RStudio Project so you can reference it with `here::here("nps_config.yaml")`.

## Setup: Load Libraries & Configuration, Set Park & Year

```{r}
# load libraries
library(npstools)
library(tidyverse)
library(here)
library(glue)

# load configuration
nps_config <- get_nps_config("~/github/nps-veg/data/nps_config.yaml")

# specify park and year of interest
park <- "CABR" # "CABR" | "CINMS" | "SABO"
year <- 2015
```

## Get Tables

### Table of Species Richness

Table E.6. Species richness (per transect) observed in 20XX monitoring of [PARK] vegetation.

```{r}
# set optional path to Excel spreadsheet output
#n_spp_xlsx <- here(glue("data/spp_richness_pivot_{park}_{year}.xlsx"))

# get species richness pivot table
n_spp_tbl <- get_n_spp_pivtbl(park, year) # , xlsx=n_spp_xlsx)

# render pivot table as html widget
n_spp_tbl$renderPivot()
```

### Table of Percent Cover

Table of data for...

Figure E.2. Absolute foliar cover (%) of plant growth forms, as observed during 20XX monitoring at CABR. Colored bars show mean values, while error bars extend ±1 s.d. from the means.

#### Render Interactive Table

```{r}
# get percent cover
pct_cover_tbl <- get_pct_cover_tbl(park, year)

# render interactive table, without Query_type column
pct_cover_tbl %>% 
  select(-Query_type) %>%
  DT::datatable() %>%
  DT::formatRound(columns=c("Average", "StdDev"), digits=3)
```

#### Render Static Table

```{r}
# render static table, for first 10 rows without Query_type column
pct_cover_tbl %>% 
  head(10) %>% 
  select(-Query_type) %>%
  knitr::kable(digits=3)
```


